An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2013-02-12 Paper.tex
Fix slanted small-caps
The 'lmodern' package overrides slanted small caps, so I removed it.  Somehow I
also started explicitly wrapping acronyms in '\textsl', so I removed those as
well.

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round,comma]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \textsl{\ols} with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \textsl{\ned} of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
    $\bar f(\beta_0)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} \bar{f}_{i} > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-\alpha$ quantile of $\max_{i \notin M_{j-1}}
    \tfrac{1}{\hat{\sigma}_i^{*}}(\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1}))$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \textsl{\mds} with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length $1$, has probability at most $\alpha$ of
    rejecting one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \textsl{\mds} with respect to
    $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
    f_i(\beta_0) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
    \infty$ (for the stationary bootstrap) or $b \to \infty$ and
    $\frac{b}{P} \to 0$ (for the moving or circular block bootstraps)
    then the procedure outlined above controls \textsl{\sfwe} at level
    $\alpha$ for the family of null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \textsl{\sfwe} at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\textsl{\ned} process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
    generated by the moving blocks, circular blocks, or stationary
    bootstrap with block lengths drawn from the geometric
    distribution, and $b$ satisfies $b \to \infty$ and $\frac{b}{P}
    \to 0$; $b$ is the block length of the moving or circular blocks
    bootstraps and is the expected block length of the stationary
    bootstrap.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$; and $\frac12 \sum_{t=1}^T h_t^* = 0$
    a.s. where $h_t^* = h(y_s^*, z_s^*, \hat\beta_T)$.  Also define
    \begin{equation}
      H_{t}^* = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
      \end{cases}
    \end{equation}
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite and $\E f_t(\beta_0) = \E
    f_s(\beta_0)$ for all $s$ and $t$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{lem}[Formalization of Remark~\ref{rem:01}]
  Suppose that the conditions of Theorem~\ref{res:2} Part~\ref{it:3}
  hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
  of $(\bar{f}_{1k}(\beta_k),\dots,\bar{f}_{mk}(\beta_k))$ is
  uniformly positive definite for each $k$.  Then the procedure
  described in Remark~\ref{rem:01} achieves \textsl{\sfwe}.
\end{lem}

>>>>

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round,comma]{natbib}
\usepackage[margin=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

@@

\begin{thm}\label{res:1}
  Suppose that we have two models $\hat{y}_{0t}$ and $\hat{y}_{1t}$ to
  forecast the variable $y_t$, and have observations for
  $t=1,\dots,T+1$.  Assume the following hold:
  \begin{enumerate}
  \item \label{item:1} The benchmark forecast $\hat{y}_{0,t+1}$, is
    estimated using \ols\ with a recursive window:
    $\hat{y}_{0,t+1} = x_t'\hat{\beta}_t$ for some vector of
    predictors $x_t$ with $\hat{\beta}_t$ given by
    Equation~\eqref{eq:8}.  Also define $\beta_0 = (\E x_{t-1}
    x_{t-1}')^{-1} \E x_{t-1} y_t$ and assume that $\beta_0$ does not depend
    on~$t$.
  \item \label{item:2} The alternative forecast, $\hat{y}_{1t}$, is
    estimated using a rolling window of fixed length $R$ (which is
    less than $T$), so $\hat{y}_{1,t+1} =
    \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})$ where $\psi$ is a known
    function and $z_t$ is a sequence of predictors that may include
    $x_t$.
  \item \label{item:3} The series $y_t$ and $z_t$ are \ned\ of size
    $-\frac12$ on a strong mixing series of size $-\frac{r}{r-2}$ for $r>2$ or a
    uniform mixing series of size $-\frac{r}{2r-2}$.  Also, $y_t$,
    $\hat{y}_{1t}$, and $x_t$ have uniformly bounded $2 r+\delta$
    moments for some positive $\delta$.
  \item \label{item:4} Define \[f_t(\beta) = (y_{t+1} - x_t'\beta)^2 -
    (y_{t+1} - \hat{y}_{1,t+1})^2 + (x_t'\beta - \hat{y}_{1,t+1})^2,\]
    $\bar{f}(\beta) = \tfrac1P \sum_{t=R+1}^T f_t(\beta)$, and $\bar f
    = \tfrac1P \sum_{t=R+1}^{T} f_t(\hat{\beta}_t)$, with $P = T - R$;
    $\bar f(\beta_0)$ has uniformly positive and finite long run
    variance.
  \end{enumerate}
  Under the null hypothesis that $y_t - \hat{y}_{0t}(\beta_0)$ is a
  martingale difference sequence with respect to the filtration
  $\mathcal{F}_t = \sigma((y_t, z_{t}), (y_{t-1}, z_{t-1}),\dots)$,
  $\tfrac{\sqrt{P}}{\hat\sigma} \bar f \to^d N(0,1)$, where 
  \begin{align*}
    \hat{\sigma}^2 &= \hat{S}_{ff} + 2 \Pi (\hat{S}_{fg} + \hat{S}_{gg}), &
    \hat{S}_{ff} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) - \bar
    f)^2, \\
    \hat{S}_{fg} &= \tfrac1P \sum_{t=R+1}^T (f_t(\hat{\beta}_t) -
    \bar{f})(g_t(\hat{\beta}_t) - \bar g)', &
    \hat{S}_{gg} &= \tfrac1P \sum_{t=R+1}^T (g_t(\hat{\beta}_t) - \bar
    g)(g_t(\hat{\beta}_t) - \bar g)',
  \end{align*}
  $\Pi = 1 - \tfrac{R}{P} \log(1 + \tfrac{P}{R})$, $\bar{g} = \tfrac1T
  \sum_{t=R+1}^T g_t(\hat{\beta}_t)$, $\X' = [x_1,\dots,x_T]$, and
  \begin{equation*}
    g_t(\beta) =
    \Big\{\tfrac{2}{P}\sum_{s=R}^T x_s (x_s'\beta - \hat{y}_{1,s+1}) \Big\}'
    \big(\tfrac1T \X'\X \big)^{-1} x_t(y_{t+1} - x_t'\beta).
  \end{equation*}
\end{thm}

@@

  Let the $*$-superscript denote a random variable with the
  distribution induced by the bootstrap of Algorithm~\ref{alg:1} and
  consider the following procedure:
  \begin{enumerate}
  \item Define $M_0 = \emptyset$ and, for $j = 1,\dots,m$, let $M_j =
    \{i : \tfrac1{\hat\sigma_i} \bar{f}_{i} > \hat{d}_j\}$, where
    $\hat{d}_j$ is the $1-\alpha$ quantile of $\max_{i \notin M_{j-1}}
    \tfrac{1}{\hat{\sigma}_i^{*}}(\bar{f}_{i}^{*} -
    \bar{f_i}(\hat{\beta}_{T+1}))$.
  \item Reject all of the models $i$ with $i \in \bigcup_{j=1}^m M_j$.
  \end{enumerate}
  The following conclusions hold:
  \begin{enumerate}[i.]
  \item\label{it:1} For each $G \subset \{1,\dots,m\}$, let
    $\mathcal{F}_t^G$ be the smallest $\sigma$-field containing
    $\mathcal{F}_{lt}$ for all $l \in G$.  Under the null hypothesis
    that $y_t - \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_t^I$ for some $I \subset \{1,\dots,m\}$, the
    procedure outlined above, but using the moving block bootstrap
    with block length $1$, has probability at most $\alpha$ of
    rejecting one or more models in $I$.
  \item\label{it:2} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is an \mds\ with respect to
    $\mathcal{F}_{lt}$ against the one-sided alternative $\E \bar
    f_i(\beta_0) > 0$.  If $p \to 0$ and $P p \to \infty$ as $T \to
    \infty$ (for the stationary bootstrap) or $b \to \infty$ and
    $\frac{b}{P} \to 0$ (for the moving or circular block bootstraps)
    then the procedure outlined above controls \sfwe\ at level
    $\alpha$ for the family of null hypotheses $H_1,\dots,H_m$.
  \item\label{it:3} Let $H_l$ be the null hypothesis that $y_t -
    \hat{y}_{0t}$ is uncorrelated with $\hat{y}_{lt}$ against the
    one-sided alternative $\E \bar f_i(\beta_0) > 0$.  If $p \to 0$
    and $P p \to \infty$ as $T \to \infty$ (for the stationary
    bootstrap) or $b \to \infty$ and $\frac{b}{P} \to 0$ (for the
    moving or circular block bootstraps) then the procedure outlined
    above controls \sfwe\ at level $\alpha$ for the family of
    null hypotheses $H_1,\dots,H_m$.
  \end{enumerate}
\end{thm}

@@

\begin{thm}\label{res:3}
  Suppose the following conditions hold:
  \begin{enumerate}
  \item Let $\{y_t, z_t\}$ be an $L_2$-\ned\ process of size $-\frac12$ on
    a strong mixing series $\{V_t\}$ of size $-\frac{r}{r-2}$, with $r
    > 2$.
  \item The sequence $(y_1^{*}, z_t^*),\dots,(y_T^{*}, z_T^*)$ is
    generated by the moving blocks, circular blocks, or stationary
    bootstrap with block lengths drawn from the geometric
    distribution, and $b$ satisfies $b \to \infty$ and $\frac{b}{P}
    \to 0$; $b$ is the block length of the moving or circular blocks
    bootstraps and is the expected block length of the stationary
    bootstrap.
  \item The estimator $\hat{\beta}_t$ of $\beta_0$ is estimated with a
    recursive, rolling, or fixed estimation window and satisfies
    $\hat{\beta}_{t} - \beta_{0} = \hat{B}_{t} H_t$; $\hat{B}_{t}$ is
    a sequence of $k$ by $q$ matrices such that $\sup_t |\hat{B}_t -
    B| \to^p 0$, $\sup_t |\hat{B}_t^{*} - B^{*}| \to^p 0$, and $B^{*}
    = B + o_p$; $H_{t}$ is a sequence of $q$-vectors such that 
    \begin{equation}
      H_{t} = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s} & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s} & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s} & \text{fixed window} \\
      \end{cases}
    \end{equation}
    $h_{s}(\beta) = h(y_{s}, z_{s}, \beta)$, $h_s = h_s(\beta_0)$, and
    $\E h_{s} = 0$ for all $s$; and $\frac12 \sum_{t=1}^T h_t^* = 0$
    a.s. where $h_t^* = h(y_s^*, z_s^*, \hat\beta_T)$.  Also define
    \begin{equation}
      H_{t}^* = \begin{cases} 
        \tfrac1t \sum_{s=1}^t h_{s}^* & \text{recursive window} \\
        \tfrac1R \sum_{s=t-R+1}^t h_{s}^* & \text{rolling window} \\
        \tfrac1R \sum_{s=1}^R h_{s}^* & \text{fixed window} \\
      \end{cases}
    \end{equation}
  \item Let $f_{t}(\beta) = f(y_{t}, z_{t}, \beta)$ be an $l$-vector;
    $\| \sup_{\beta \in N} f_{t}(\beta) \|_{r+\delta}$ and $\|
    \sup_{\beta \in N} h_{t}(\beta) \|_{r+\delta}$ are uniformly
    finite in $t$, where $N$ is an open neighborhood of $\beta_{0}$.
  \item Each element of $\E f_{t}(\beta)$ is continuously
    differentiable in the neighborhood $N$.  Moreover, $\sup_{\beta
      \in N} | F_{t}(\beta) |$ is uniformly finite in $t$ with
    $F_{t}(\beta) = \dd{\beta'} \E f_{t}(\beta)$.
  \item There exist finite constants $C$, $\phi > 0$, and $Q \geq r$
    such that \[\sup_{\epsilon : N(\beta_{0}, \epsilon) \subset N}\|
    \sup_{\beta \in N(\beta_{0}, \epsilon)} f_{t}(\beta) - f_{t} \|_Q
    \leq C \epsilon^{\phi}\] and \[\sup_{\epsilon : N(\beta_{0},
      \epsilon) \subset N}\| \sup_{\beta \in N(\beta_{0}, \epsilon)}
    h_{t}(\beta) - h_{t} \|_Q \leq C \epsilon^{\phi},\] where
    $N(\beta, \epsilon) = \{b : |b - \beta| < \epsilon\}$.
  \item $R, P \to \infty$ as $T \to \infty$.
  \item The asymptotic variance matrix of $\bar{f}(\beta_0)$ is
    uniformly positive definite and $\E f_t(\beta_0) = \E
    f_s(\beta_0)$ for all $s$ and $t$.
  \end{enumerate}
  Then
  \begin{equation}
    \pr[\sup_x | \pr^*[\sqrt{P} (\bar{f}^* - \bar{f}(\hat{\beta}_{T}))
        \leq x] - \pr[\sqrt{P}( \bar{f} - \E \bar{f}(\beta_0)) \leq x] | >
      \epsilon] \to 0
  \end{equation}
  for all $\epsilon > 0$.
\end{thm}

@@

\begin{lem}[Formalization of Remark~\ref{rem:01}]
  Suppose that the conditions of Theorem~\ref{res:2} Part~\ref{it:3}
  hold but $f_i = (f_{i1},\dots,f_{iq})$ and the asymptotic variance
  of $(\bar{f}_{1k}(\beta_k),\dots,\bar{f}_{mk}(\beta_k))$ is
  uniformly positive definite for each $k$.  Then the procedure
  described in Remark~\ref{rem:01} achieves \sfwe.
\end{lem}
